---
title: "Preprocessing.Rmd"
author: "Christopher Himmel"
date: "February 8, 2019"
output: word_document
---

#Introduction

This document is in excerpt from the original Sales_Prediction, removed and put in its own document for readability. Here we go through each feature and show a bargraph, determining whether there is any information available in the feature to contribute to the model.


#Set up R environment

```{r, message=FALSE}
library(tm)
library(dplyr)
library(wordcloud)
library(SnowballC)
library(corrplot)
library(rpart)
library(rattle)
library(randomForest)
library(tidyr)
library(ggplot2)
setwd("C:/Users/Christopher/Dropbox/Deep Learning/Projects/Sales-Prediction")
```

#Upload data pulled out of MMS

Load and view Item Master (INVMST):

```{r}
Item_Master = read.csv("data/INVMST - Item Master.csv")
View(Item_Master)
summary(Item_Master)
```

Load and view Chain Level Inventory Balance file (INVCBL):

```{r}
Inv_Bal_Chain = read.csv("data/INVCBL - Chain Level Inventory Balance Data.csv")
View(Inv_Bal_Chain)
summary(Inv_Bal_Chain)
```

Load and view Store Level Inventory Balance file, filtered for Niquea'D stores (INVBAL):

```{r}
Inv_Bal_Store = read.csv("data/INVBAL - Store Level Inventory Balance Data - Niquea'D.csv")
View(Inv_Bal_Store)
summary(Inv_Bal_Store)
```

#Format data set

Create chain level field with combined regular sales and advertised sales:

```{r}
Inv_Bal_Chain_mut <-
	Inv_Bal_Chain %>%
	mutate(chn_sales=CBRSUY+CBASUY)
```

Create total Niquea'D summarized sales with combined regular sales and advertised sales:

```{r}
Inv_Bal_Store_sum <- 
	Inv_Bal_Store %>%
	group_by(INUMBR) %>%
	summarise(nd_sales=sum(IBRSUY+IBASUY),
	          IBHAND_sum=sum(IBHAND),
	          IBWKCR_sum=sum(IBWKCR),
	          IBWK01_sum=sum(IBWK01),
	          IBWK02_sum=sum(IBWK02),
	          IBWK03_sum=sum(IBWK03),
	          IBWK04_sum=sum(IBWK04),
	          IBWK05_sum=sum(IBWK05),
	          IBWK06_sum=sum(IBWK06),
	          IBWK07_sum=sum(IBWK07),
	          IBWK08_sum=sum(IBWK08))
Inv_Bal_Store_sum <- subset(Inv_Bal_Store_sum, IBHAND_sum!=0 | nd_sales!=0)
```

Combine two new sales numbers into one file by SKU:

```{r}
Inv_values <-
	Inv_Bal_Store_sum %>%
	left_join(Inv_Bal_Chain_mut, by="INUMBR") %>%
	select(INUMBR,nd_sales,chn_sales,IBHAND_sum,IBWKCR_sum,IBWK01_sum,IBWK02_sum,IBWK03_sum,IBWK04_sum,
	       IBWK05_sum,IBWK06_sum,IBWK07_sum,IBWK08_sum)
```

Combine SKU, sales data into one file for analysis:

```{r}
Inv_final <-
	Inv_values %>%
	left_join(Item_Master, by="INUMBR")
```

#Test each attribute for significant amount of data

Visualize each column of data:

```{r}
# IDESCR - factors of descriptions
# ICHECK - all Zeros
barplot(table(Inv_final$ICHECK),main="ICHECK")
# IDSCCD - minimal values
barplot(table(Inv_final$IDSCCD),main="IDSCCD")
# ISORT - factors of descriptions
# ISTYLN - all NA's
# ASNUM - distributed values
barplot(table(Inv_final$ASNUM),main="ASNUM")
# IVNDPN - empty
barplot(table(Inv_final$IVNDPN),main="IVNDPN")
# IMFGR - empty
barplot(table(Inv_final$IMFGR),main="IMFGR")
# IMFGNO - some values
barplot(table(Inv_final$IMFGNO),main="IMFGNO")
# IDEPT - use
barplot(table(Inv_final$IDEPT),main="IDEPT")
# ISDEPT - use
barplot(table(Inv_final$ISDEPT),main="ISDEPT")
# ICLAS - use
barplot(table(Inv_final$ICLAS),main="ICLAS")
# ISCLAS - use
barplot(table(Inv_final$ISCLAS),main="ISCLAS")
# BYRNUM - convert NA's to 0
Inv_final$BYRNUM[is.na(Inv_final$BYRNUM)]<-0
barplot(table(Inv_final$BYRNUM),main="BYRNUM")
# IASPAC - empty
barplot(table(Inv_final$IASPAC),main="IASPAC")
# IADVYN - empty
barplot(table(Inv_final$IADVYN),main="IADVYN")
# IBUYCD - mostly empty
barplot(table(Inv_final$IBUYCD),main="IBUYCD")
# ISET - empty
barplot(table(Inv_final$ISET),main="ISET")
# IWARNT - mostly empty
barplot(table(Inv_final$IWARNT),main="IWARNT")
# IPRMPT - mostly empty
barplot(table(Inv_final$IPRMPT),main="IPRMPT")
# IPRVNT - mostly empty
barplot(table(Inv_final$IPRVNT),main="IPRVNT")
# ITKTTR - convert NA's to 0
Inv_final$ITKTTR[is.na(Inv_final$ITKTTR)]<-0
barplot(table(Inv_final$ITKTTR),main="ITKTTR")
# ITKTTA - mostly empty
barplot(table(Inv_final$ITKTTA),main="ITKTTA")
# ITKTN
barplot(table(Inv_final$ITKTN),main="ITKTN")
# ILBLTR - convert NA's to 0
Inv_final$ILBLTR[is.na(Inv_final$ILBLTR)]<-0
barplot(table(Inv_final$ILBLTR),main="ILBLTR")
# ILBLTA - empty
barplot(table(Inv_final$ILBLTA),main="ILBLTA")
# IFINLN
barplot(table(Inv_final$IFINLN),main="IFINLN")
# IPROFL - mostly empty
barplot(table(Inv_final$IPROFL),main="IPROFL")
# IMODUL - mostly empty
barplot(table(Inv_final$IMODUL),main="IMODUL")
# ISTYPE
barplot(table(Inv_final$ISTYPE),main="ISTYPE")
# ISCOLR - mostly empty
barplot(table(Inv_final$ISCOLR),main="ISCOLR")
# ISSIZE - mostly empty
barplot(table(Inv_final$ISSIZE),main="ISSIZE")
# IHAZCD - all NA's
# MCHNUM - all NA's
# ISUBST - empty
barplot(table(Inv_final$ISUBST),main="ISUBST")
# ICORE - empty
barplot(table(Inv_final$ICORE),main="ICORE")
# IREPL - empty
barplot(table(Inv_final$IREPL),main="IREPL")
# ISLUM - mostly empty
barplot(table(Inv_final$ISLUM),main="ISLUM")
# IUMCV2 - all 1's
barplot(table(Inv_final$IUMCV2),main="IUMCV2")
# IBYUM - all EA's
barplot(table(Inv_final$IBYUM),main="IBYUM")
# IMINPK
barplot(table(Inv_final$IMINPK),main="IMINPK")
# ISTDPK
barplot(table(Inv_final$ISTDPK),main="ISTDPK")
# IHLDOR - mostly empty
barplot(table(Inv_final$IHLDOR),main="IHLDOR")
# IMOQTY - mostly empty
barplot(table(Inv_final$IMOQTY),main="IMOQTY")
# IMNSTK - empty
barplot(table(Inv_final$IMNSTK),main="IMNSTK")
# IMXSTK
barplot(table(Inv_final$IMXSTK),main="IMXSTK")
# IMDSTK - empty
barplot(table(Inv_final$IMDSTK),main="IMDSTK")
# IDSPLY
barplot(table(Inv_final$IDSPLY),main="IDSPLY")
# IOMULT - mostly empty
barplot(table(Inv_final$IOMULT),main="IOMULT")
# IRPLCD - convert NA's to 0
Inv_final$IRPLCD[is.na(Inv_final$IRPLCD)]<-0
barplot(table(Inv_final$IRPLCD),main="IRPLCD")
# IMFPRC - empty
barplot(table(Inv_final$IMFPRC),main="IMFPRC")
# IWGHT - there is one outlier that throws the significance off
barplot(table(Inv_final$IWGHT),main="IWGHT")
Inv_final$IWGHT[Inv_final$IWGHT==3001.4]=0
# ICUBE - investigate taking the log(ICUBE)
barplot(table(Inv_final$ICUBE),main="ICUBE")
# IDLGTH - investigate taking the log(ICUBE)
barplot(table(Inv_final$IDLGTH),main="IDLGTH")
# IDWDTH - investigate taking the log(ICUBE)
barplot(table(Inv_final$IDWDTH),main="IDWDTH")
# IDHGHT - investigate taking the log(ICUBE)
barplot(table(Inv_final$IDHGHT),main="IDHGHT")
# IMDATE
barplot(table(Inv_final$IMDATE),main="IMDATE")
# IMCENT - empty
barplot(table(Inv_final$IMCENT),main="IMCENT")
# IVPLTI - not significant
barplot(table(Inv_final$IVPLTI),main="IVPLTI")
# IVPLHI
barplot(table(Inv_final$IVPLHI),main="IVPLHI")
# SHPNUM - empty
barplot(table(Inv_final$SHPNUM),main="SHPNUM")

# Lots of NA's in IDISTM, replace with 0
Inv_final$IDISTM[is.na(Inv_final$IDISTM)]<-0
barplot(table(Inv_final$IDISTM),main="IDISTM")

# IHLDWO - empty
barplot(table(Inv_final$IHLDWO),main="IHLDWO")
# IIGNUM - empty
barplot(table(Inv_final$IIGNUM),main="IIGNUM")
# ISDIM - empty
barplot(table(Inv_final$ISDIM),main="ISDIM")
# IVATCD - all NA's
# IPLAN - empty
barplot(table(Inv_final$IPLAN),main="IPLAN")
# IVLRK1 - empty
barplot(table(Inv_final$IVLRK1),main="IVLRK1")
# IVLRK2 - empty
barplot(table(Inv_final$IVLRK2),main="IVLRK2")
# IVLRK3 - all NA's
# IVLRK4 - all NA's
# IRPLCN - empty
barplot(table(Inv_final$IRPLCN),main="IRPLCN")
# IRPLDT - empty
barplot(table(Inv_final$IRPLDT),main="IRPLDT")
# ISEASN
barplot(table(Inv_final$ISEASN),main="ISEASN")
# IDEADC
barplot(table(Inv_final$IDEADC),main="IDEADC")
# IDEADD - empty
barplot(table(Inv_final$IDEADD),main="IDEADD")
# INLRTL
barplot(table(Inv_final$INLRTL),main="INLRTL")
# IHANDL is all NA's
# IATRB1 - empty
barplot(table(Inv_final$IATRB1),main="IATRB1")
# IATRB2 - empty
barplot(table(Inv_final$IATRB2),main="IATRB2")
# IATRB3
barplot(table(Inv_final$IATRB3),main="IATRB3")
# IATRB4 - empty
barplot(table(Inv_final$IATRB4),main="IATRB4")
# IATRB5 - all N's
barplot(table(Inv_final$IATRB5),main="IATRB5")
# IPRCCH
barplot(table(Inv_final$IPRCCH),main="IPRCCH")
# IPRCZN - all N's
barplot(table(Inv_final$IPRCZN),main="IPRCZN")
# IPRCST
barplot(table(Inv_final$IPRCST),main="IPRCST")
# IASNUM - empty
barplot(table(Inv_final$IASNUM),main="IASNUM")
# ICORGP
barplot(table(Inv_final$ICORGP),main="ICORGP")
# ILEAD
barplot(table(Inv_final$ILEAD),main="ILEAD")
# IHZCOD - all NA's
# IFRACT - all NA's
# IMCRDT - distributed
barplot(table(Inv_final$IMCRDT),main="IMCRDT")
# IMCRCN - all 1's
barplot(table(Inv_final$IMCRCN),main="IMCRCN")
```
